Performances Code

### 2019-02-19 Scripts/performances.rmd
added to results script

all10kbresults <- data.frame(Resampling=c(rep("None", 8),
                                       rep("RUS", 8),
                                       rep("ROS", 8),
                                       rep("SMOTE", 8),
                                       rep("ROSE", 8)),
                          CL=rep(c(rep("GM12878",4),
                               rep("K562", 4)),5),
                          Metric=rep(c("Accuracy", "AUPRC", "F1-Score", "MCC"), 10))

all10kbresults$Performance <- c(round(rfperf_gm12878_10kb_none[9,2],2),
                                round(rfperf_gm12878_10kb_none[19,2],2),
                                round(rfperf_gm12878_10kb_none[16,2],2),
                                round(rfperf_gm12878_10kb_none[15,2],2),
                                round(rfperf_K562_10kb_none[9,2],2),
                                round(rfperf_K562_10kb_none[19,2],2),
                                round(rfperf_K562_10kb_none[16,2],2),
                                round(rfperf_K562_10kb_none[15,2],2),
                                round(mean(rfperf_gm12878_10kb_rus[9,]),2),
                                round(mean(rfperf_gm12878_10kb_rus[19,]),2),
                                round(mean(rfperf_gm12878_10kb_rus[16,]),2),
                                round(mean(rfperf_gm12878_10kb_rus[15,]),2),
                                round(mean(rfperf_K562_10kb_rus[9,]),2),
                                round(mean(rfperf_K562_10kb_rus[19,]),2),
                                round(mean(rfperf_K562_10kb_rus[16,]),2),
                                round(mean(rfperf_K562_10kb_rus[15,]),2),
                                round(mean(rfperf_gm12878_10kb_ros[9,]),2),
                                round(mean(rfperf_gm12878_10kb_ros[19,]),2),
                                round(mean(rfperf_gm12878_10kb_ros[16,]),2),
                                round(mean(rfperf_gm12878_10kb_ros[15,]),2),
                                round(mean(rfperf_K562_10kb_ros[9,]),2),
                                round(mean(rfperf_K562_10kb_ros[19,]),2),
                                round(mean(rfperf_K562_10kb_ros[16,]),2),
                                round(mean(rfperf_K562_10kb_ros[15,]),2),
                                round(mean(rfperf_gm12878_10kb_smote[9,]),2),
                                round(mean(rfperf_gm12878_10kb_smote[19,]),2),
                                round(mean(rfperf_gm12878_10kb_smote[16,]),2),
                                round(mean(rfperf_gm12878_10kb_smote[15,]),2),
                                round(mean(rfperf_K562_10kb_smote[9,]),2),
                                round(mean(rfperf_K562_10kb_smote[19,]),2),
                                round(mean(rfperf_K562_10kb_smote[16,]),2),
                                round(mean(rfperf_K562_10kb_smote[15,]),2),
                                round(mean(rfperf_gm12878_10kb_rose[9,]),2),
                                round(mean(rfperf_gm12878_10kb_rose[19,]),2),
                                round(mean(rfperf_gm12878_10kb_rose[16,]),2),
                                round(mean(rfperf_gm12878_10kb_rose[15,]),2),
                                round(mean(rfperf_K562_10kb_rose[9,]),2),
                                round(mean(rfperf_K562_10kb_rose[19,]),2),
                                round(mean(rfperf_K562_10kb_rose[16,]),2),
                                round(mean(rfperf_K562_10kb_rose[15,]),2))

@@

@@

all25kbresults <- data.frame(Resampling=c(rep("None", 8),
                                       rep("RUS", 8),
                                       rep("ROS", 8),
                                       rep("SMOTE", 8),
                                       rep("ROSE", 8)),
                          CL=rep(c(rep("GM12878",4),
                               rep("K562", 4)),5),
                          Metric=rep(c("Accuracy", "AUPRC", "F1-Score", "MCC"), 10))

all25kbresults$Performance <- c(round(rfperf_gm12878_25kb_none[9,2],2),
                                round(rfperf_gm12878_25kb_none[19,2],2),
                                round(rfperf_gm12878_25kb_none[16,2],2),
                                round(rfperf_gm12878_25kb_none[15,2],2),
                                round(rfperf_K562_25kb_none[9,2],2),
                                round(rfperf_K562_25kb_none[19,2],2),
                                round(rfperf_K562_25kb_none[16,2],2),
                                round(rfperf_K562_25kb_none[15,2],2),
                                round(mean(rfperf_gm12878_25kb_rus[9,]),2),
                                round(mean(rfperf_gm12878_25kb_rus[19,]),2),
                                round(mean(rfperf_gm12878_25kb_rus[16,]),2),
                                round(mean(rfperf_gm12878_25kb_rus[15,]),2),
                                round(mean(rfperf_K562_25kb_rus[9,]),2),
                                round(mean(rfperf_K562_25kb_rus[19,]),2),
                                round(mean(rfperf_K562_25kb_rus[16,]),2),
                                round(mean(rfperf_K562_25kb_rus[15,]),2),
                                round(mean(rfperf_gm12878_25kb_ros[9,]),2),
                                round(mean(rfperf_gm12878_25kb_ros[19,]),2),
                                round(mean(rfperf_gm12878_25kb_ros[16,]),2),
                                round(mean(rfperf_gm12878_25kb_ros[15,]),2),
                                round(mean(rfperf_K562_25kb_ros[9,]),2),
                                round(mean(rfperf_K562_25kb_ros[19,]),2),
                                round(mean(rfperf_K562_25kb_ros[16,]),2),
                                round(mean(rfperf_K562_25kb_ros[15,]),2),
                                round(mean(rfperf_gm12878_25kb_smote[9,]),2),
                                round(mean(rfperf_gm12878_25kb_smote[19,]),2),
                                round(mean(rfperf_gm12878_25kb_smote[16,]),2),
                                round(mean(rfperf_gm12878_25kb_smote[15,]),2),
                                round(mean(rfperf_K562_25kb_smote[9,]),2),
                                round(mean(rfperf_K562_25kb_smote[19,]),2),
                                round(mean(rfperf_K562_25kb_smote[16,]),2),
                                round(mean(rfperf_K562_25kb_smote[15,]),2),
                                round(mean(rfperf_gm12878_25kb_rose[9,]),2),
                                round(mean(rfperf_gm12878_25kb_rose[19,]),2),
                                round(mean(rfperf_gm12878_25kb_rose[16,]),2),
                                round(mean(rfperf_gm12878_25kb_rose[15,]),2),
                                round(mean(rfperf_K562_25kb_rose[9,]),2),
                                round(mean(rfperf_K562_25kb_rose[19,]),2),
                                round(mean(rfperf_K562_25kb_rose[16,]),2),
                                round(mean(rfperf_K562_25kb_rose[15,]),2))

@@

@@

all50kbresults <- data.frame(Resampling=c(rep("None", 8),
                                       rep("RUS", 8),
                                       rep("ROS", 8),
                                       rep("SMOTE", 8),
                                       rep("ROSE", 8)),
                          CL=rep(c(rep("GM12878",4),
                               rep("K562", 4)),5),
                          Metric=rep(c("Accuracy", "AUPRC", "F1-Score", "MCC"), 10))

all50kbresults$Performance <- c(round(rfperf_gm12878_50kb_none[9,2],2),
                                round(rfperf_gm12878_50kb_none[19,2],2),
                                round(rfperf_gm12878_50kb_none[16,2],2),
                                round(rfperf_gm12878_50kb_none[15,2],2),
                                round(rfperf_K562_50kb_none[9,2],2),
                                round(rfperf_K562_50kb_none[19,2],2),
                                round(rfperf_K562_50kb_none[16,2],2),
                                round(rfperf_K562_50kb_none[15,2],2),
                                round(mean(rfperf_gm12878_50kb_rus[9,]),2),
                                round(mean(rfperf_gm12878_50kb_rus[19,]),2),
                                round(mean(rfperf_gm12878_50kb_rus[16,]),2),
                                round(mean(rfperf_gm12878_50kb_rus[15,]),2),
                                round(mean(rfperf_K562_50kb_rus[9,]),2),
                                round(mean(rfperf_K562_50kb_rus[19,]),2),
                                round(mean(rfperf_K562_50kb_rus[16,]),2),
                                round(mean(rfperf_K562_50kb_rus[15,]),2),
                                round(mean(rfperf_gm12878_50kb_ros[9,]),2),
                                round(mean(rfperf_gm12878_50kb_ros[19,]),2),
                                round(mean(rfperf_gm12878_50kb_ros[16,]),2),
                                round(mean(rfperf_gm12878_50kb_ros[15,]),2),
                                round(mean(rfperf_K562_50kb_ros[9,]),2),
                                round(mean(rfperf_K562_50kb_ros[19,]),2),
                                round(mean(rfperf_K562_50kb_ros[16,]),2),
                                round(mean(rfperf_K562_50kb_ros[15,]),2),
                                round(mean(rfperf_gm12878_50kb_smote[9,]),2),
                                round(mean(rfperf_gm12878_50kb_smote[19,]),2),
                                round(mean(rfperf_gm12878_50kb_smote[16,]),2),
                                round(mean(rfperf_gm12878_50kb_smote[15,]),2),
                                round(mean(rfperf_K562_50kb_smote[9,]),2),
                                round(mean(rfperf_K562_50kb_smote[19,]),2),
                                round(mean(rfperf_K562_50kb_smote[16,]),2),
                                round(mean(rfperf_K562_50kb_smote[15,]),2),
                                round(mean(rfperf_gm12878_50kb_rose[9,]),2),
                                round(mean(rfperf_gm12878_50kb_rose[19,]),2),
                                round(mean(rfperf_gm12878_50kb_rose[16,]),2),
                                round(mean(rfperf_gm12878_50kb_rose[15,]),2),
                                round(mean(rfperf_K562_50kb_rose[9,]),2),
                                round(mean(rfperf_K562_50kb_rose[19,]),2),
                                round(mean(rfperf_K562_50kb_rose[16,]),2),
                                round(mean(rfperf_K562_50kb_rose[15,]),2))

all50kbresults$Resampling <- factor(all50kbresults$Resampling, levels=c("None", "RUS", "ROS", "SMOTE", "ROSE"))
all50kbresults$CL <- factor(all50kbresults$CL, levels=c("GM12878", "K562"))
all50kbresults$Metric <- factor(all50kbresults$Metric, levels=c("Accuracy", "AUPRC", "F1-Score", "MCC"))

@@

@@

all100kbresults <- data.frame(Resampling=c(rep("None", 8),
                                       rep("RUS", 8),
                                       rep("ROS", 8),
                                       rep("SMOTE", 8),
                                       rep("ROSE", 8)),
                          CL=rep(c(rep("GM12878",4),
                               rep("K562", 4)),5),
                          Metric=rep(c("Accuracy", "AUPRC", "F1-Score", "MCC"), 10))

>>>>

all10kbresults <- data.frame(Resampling=c(rep("None", 12),
                                       rep("RUS", 12),
                                       rep("ROS", 12),
                                       rep("SMOTE", 12),
                                       rep("ROSE", 12)),
                          CL=rep(c(rep("GM12878",6),
                               rep("K562", 6)),5),
                          Metric=rep(c("Accuracy", 
                                       "AUPRC", 
                                       "F1-Score", 
                                       "MCC",
                                       "Informedness",
                                       "Balanced Acc"), 10))

all10kbresults$Performance <- c(round(rfperf_gm12878_10kb_none[9,2],2), #accuracy
                                round(rfperf_gm12878_10kb_none[19,2],2), #auprc
                                round(rfperf_gm12878_10kb_none[16,2],2), #f1
                                round(rfperf_gm12878_10kb_none[15,2],2), #mcc
								round(rfperf_gm12878_10kb_none[18,2],2), #youden
								(round(rfperf_gm12878_10kb_none[6,2],2) + round(rfperf_gm12878_10kb_none[7,2],2))/2, #balanced accuracy

                                round(rfperf_K562_10kb_none[9,2],2),
                                round(rfperf_K562_10kb_none[19,2],2),
                                round(rfperf_K562_10kb_none[16,2],2),
                                round(rfperf_K562_10kb_none[15,2],2),
								round(rfperf_K562_10kb_none[18,2],2),
								(round(rfperf_K562_10kb_none[6,2],2) + round(rfperf_K562_10kb_none[7,2],2))/2,

                                round(mean(rfperf_gm12878_10kb_rus[9,1]),2),
                                round(mean(rfperf_gm12878_10kb_rus[19,1]),2),
                                round(mean(rfperf_gm12878_10kb_rus[16,1]),2),
                                round(mean(rfperf_gm12878_10kb_rus[15,1]),2),
								round(mean(rfperf_gm12878_10kb_rus[18,1]),2),
								(round(mean(rfperf_gm12878_10kb_rus[6,1]),2) + round(mean(rfperf_gm12878_10kb_rus[7,1]),2))/2,

                                round(mean(rfperf_K562_10kb_rus[9,1]),2),
                                round(mean(rfperf_K562_10kb_rus[19,1]),2),
                                round(mean(rfperf_K562_10kb_rus[16,1]),2),
                                round(mean(rfperf_K562_10kb_rus[15,1]),2),
								round(mean(rfperf_K562_10kb_rus[18,1]),2),
								(round(mean(rfperf_K562_10kb_rus[6,1]),2) + round(mean(rfperf_K562_10kb_rus[7,1]),2))/2,

                                round(mean(rfperf_gm12878_10kb_ros[9,1]),2),
                                round(mean(rfperf_gm12878_10kb_ros[19,1]),2),
                                round(mean(rfperf_gm12878_10kb_ros[16,1]),2),
                                round(mean(rfperf_gm12878_10kb_ros[15,1]),2),
								round(mean(rfperf_gm12878_10kb_ros[18,1]),2),
								(round(mean(rfperf_gm12878_10kb_ros[6,1]),2) + round(mean(rfperf_gm12878_10kb_ros[7,1]),2))/2,

                                round(mean(rfperf_K562_10kb_ros[9,1]),2),
                                round(mean(rfperf_K562_10kb_ros[19,1]),2),
                                round(mean(rfperf_K562_10kb_ros[16,1]),2),
                                round(mean(rfperf_K562_10kb_ros[15,1]),2),
								round(mean(rfperf_K562_10kb_ros[18,1]),2),
								(round(mean(rfperf_K562_10kb_ros[6,1]),2) + round(mean(rfperf_K562_10kb_ros[7,1]),2))/2,

                                round(mean(rfperf_gm12878_10kb_smote[9,1]),2),
                                round(mean(rfperf_gm12878_10kb_smote[19,1]),2),
                                round(mean(rfperf_gm12878_10kb_smote[16,1]),2),
                                round(mean(rfperf_gm12878_10kb_smote[15,1]),2),
								round(mean(rfperf_gm12878_10kb_smote[18,1]),2),
								(round(mean(rfperf_gm12878_10kb_smote[6,1]),2) + round(mean(rfperf_gm12878_10kb_smote[7,1]),2))/2,

                                round(mean(rfperf_K562_10kb_smote[9,1]),2),
                                round(mean(rfperf_K562_10kb_smote[19,1]),2),
                                round(mean(rfperf_K562_10kb_smote[16,1]),2),
                                round(mean(rfperf_K562_10kb_smote[15,1]),2),
								round(mean(rfperf_K562_10kb_smote[18,1]),2),
								(round(mean(rfperf_K562_10kb_smote[6,1]),2) + round(mean(rfperf_K562_10kb_smote[7,1]),2))/2,

                                round(mean(rfperf_gm12878_10kb_rose[9,1]),2),
                                round(mean(rfperf_gm12878_10kb_rose[19,1]),2),
                                round(mean(rfperf_gm12878_10kb_rose[16,1]),2),
                                round(mean(rfperf_gm12878_10kb_rose[15,1]),2),
								round(mean(rfperf_gm12878_10kb_rose[18,1]),2),
								(round(mean(rfperf_gm12878_10kb_rose[6,1]),2) + round(mean(rfperf_gm12878_10kb_rose[7,1]),2))/2,

                                round(mean(rfperf_K562_10kb_rose[9,1]),2),
                                round(mean(rfperf_K562_10kb_rose[19,1]),2),
                                round(mean(rfperf_K562_10kb_rose[16,1]),2),
                                round(mean(rfperf_K562_10kb_rose[15,1]),2),
								round(mean(rfperf_K562_10kb_rose[18,1]),2),
								(round(mean(rfperf_K562_10kb_rose[6,1]),2) + round(mean(rfperf_K562_10kb_rose[7,1]),2))/2)

@@

#comparing only informedness and balanced accuracy
informBA10kbplot <- ggplot(all10kbresults[which(all10kbresults$Metric=="Informedness" |
                                               all10kbresults$Metric=="Balanced Acc"),],
                       aes(x=Resampling, y=Performance, fill=CL)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  ylim(0,.8)+
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Cell Line")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

@@

all25kbresults <- data.frame(Resampling=c(rep("None", 12),
                                       rep("RUS", 12),
                                       rep("ROS", 12),
                                       rep("SMOTE", 12),
                                       rep("ROSE", 12)),
                          CL=rep(c(rep("GM12878",6),
                               rep("K562", 6)),5),
                          Metric=rep(c("Accuracy", 
                                       "AUPRC", 
                                       "F1-Score", 
                                       "MCC",
                                       "Informedness",
                                       "Balanced Acc"), 10))

all25kbresults$Performance <- c(round(rfperf_gm12878_25kb_none[9,2],2), #accuracy
                                round(rfperf_gm12878_25kb_none[19,2],2), #auprc
                                round(rfperf_gm12878_25kb_none[16,2],2), #f1
                                round(rfperf_gm12878_25kb_none[15,2],2), #mcc
								round(rfperf_gm12878_25kb_none[18,2],2), #youden
								(round(rfperf_gm12878_25kb_none[6,2],2) + round(rfperf_gm12878_25kb_none[7,2],2))/2, #balanced accuracy

                                round(rfperf_K562_25kb_none[9,2],2),
                                round(rfperf_K562_25kb_none[19,2],2),
                                round(rfperf_K562_25kb_none[16,2],2),
                                round(rfperf_K562_25kb_none[15,2],2),
								round(rfperf_K562_25kb_none[18,2],2),
								(round(rfperf_K562_25kb_none[6,2],2) + round(rfperf_K562_25kb_none[7,2],2))/2,

                                round(mean(rfperf_gm12878_25kb_rus[9,1]),2),
                                round(mean(rfperf_gm12878_25kb_rus[19,1]),2),
                                round(mean(rfperf_gm12878_25kb_rus[16,1]),2),
                                round(mean(rfperf_gm12878_25kb_rus[15,1]),2),
								round(mean(rfperf_gm12878_25kb_rus[18,1]),2),
								(round(mean(rfperf_gm12878_25kb_rus[6,1]),2) + round(mean(rfperf_gm12878_25kb_rus[7,1]),2))/2,

                                round(mean(rfperf_K562_25kb_rus[9,1]),2),
                                round(mean(rfperf_K562_25kb_rus[19,1]),2),
                                round(mean(rfperf_K562_25kb_rus[16,1]),2),
                                round(mean(rfperf_K562_25kb_rus[15,1]),2),
								round(mean(rfperf_K562_25kb_rus[18,1]),2),
								(round(mean(rfperf_K562_25kb_rus[6,1]),2) + round(mean(rfperf_K562_25kb_rus[7,1]),2))/2,

                                round(mean(rfperf_gm12878_25kb_ros[9,1]),2),
                                round(mean(rfperf_gm12878_25kb_ros[19,1]),2),
                                round(mean(rfperf_gm12878_25kb_ros[16,1]),2),
                                round(mean(rfperf_gm12878_25kb_ros[15,1]),2),
								round(mean(rfperf_gm12878_25kb_ros[18,1]),2),
								(round(mean(rfperf_gm12878_25kb_ros[6,1]),2) + round(mean(rfperf_gm12878_25kb_ros[7,1]),2))/2,

                                round(mean(rfperf_K562_25kb_ros[9,1]),2),
                                round(mean(rfperf_K562_25kb_ros[19,1]),2),
                                round(mean(rfperf_K562_25kb_ros[16,1]),2),
                                round(mean(rfperf_K562_25kb_ros[15,1]),2),
								round(mean(rfperf_K562_25kb_ros[18,1]),2),
								(round(mean(rfperf_K562_25kb_ros[6,1]),2) + round(mean(rfperf_K562_25kb_ros[7,1]),2))/2,

                                round(mean(rfperf_gm12878_25kb_smote[9,1]),2),
                                round(mean(rfperf_gm12878_25kb_smote[19,1]),2),
                                round(mean(rfperf_gm12878_25kb_smote[16,1]),2),
                                round(mean(rfperf_gm12878_25kb_smote[15,1]),2),
								round(mean(rfperf_gm12878_25kb_smote[18,1]),2),
								(round(mean(rfperf_gm12878_25kb_smote[6,1]),2) + round(mean(rfperf_gm12878_25kb_smote[7,1]),2))/2,

                                round(mean(rfperf_K562_25kb_smote[9,1]),2),
                                round(mean(rfperf_K562_25kb_smote[19,1]),2),
                                round(mean(rfperf_K562_25kb_smote[16,1]),2),
                                round(mean(rfperf_K562_25kb_smote[15,1]),2),
								round(mean(rfperf_K562_25kb_smote[18,1]),2),
								(round(mean(rfperf_K562_25kb_smote[6,1]),2) + round(mean(rfperf_K562_25kb_smote[7,1]),2))/2,

                                round(mean(rfperf_gm12878_25kb_rose[9,1]),2),
                                round(mean(rfperf_gm12878_25kb_rose[19,1]),2),
                                round(mean(rfperf_gm12878_25kb_rose[16,1]),2),
                                round(mean(rfperf_gm12878_25kb_rose[15,1]),2),
								round(mean(rfperf_gm12878_25kb_rose[18,1]),2),
								(round(mean(rfperf_gm12878_25kb_rose[6,1]),2) + round(mean(rfperf_gm12878_25kb_rose[7,1]),2))/2,

                                round(mean(rfperf_K562_25kb_rose[9,1]),2),
                                round(mean(rfperf_K562_25kb_rose[19,1]),2),
                                round(mean(rfperf_K562_25kb_rose[16,1]),2),
                                round(mean(rfperf_K562_25kb_rose[15,1]),2),
								round(mean(rfperf_K562_25kb_rose[18,1]),2),
								(round(mean(rfperf_K562_25kb_rose[6,1]),2) + round(mean(rfperf_K562_25kb_rose[7,1]),2))/2)

@@

#comparing only informedness and balanced accuracy
informBA25kbplot <- ggplot(all25kbresults[which(all25kbresults$Metric=="Informedness" |
                                               all25kbresults$Metric=="Balanced Acc"),],
                       aes(x=Resampling, y=Performance, fill=CL)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("Resampling Technique") +
  ylim(0,.8)+
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Cell Line")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

@@

all50kbresults <- data.frame(Resampling=c(rep("None", 12),
                                       rep("RUS", 12),
                                       rep("ROS", 12),
                                       rep("SMOTE", 12),
                                       rep("ROSE", 12)),
                          CL=rep(c(rep("GM12878",6),
                               rep("K562", 6)),5),
                          Metric=rep(c("Accuracy", 
                                       "AUPRC", 
                                       "F1-Score", 
                                       "MCC",
                                       "Informedness",
                                       "Balanced Acc"), 10))

all50kbresults$Performance <- c(round(rfperf_gm12878_50kb_none[9,2],2), #accuracy
                                round(rfperf_gm12878_50kb_none[19,2],2), #auprc
                                round(rfperf_gm12878_50kb_none[16,2],2), #f1
                                round(rfperf_gm12878_50kb_none[15,2],2), #mcc
								round(rfperf_gm12878_50kb_none[18,2],2), #youden
								(round(rfperf_gm12878_50kb_none[6,2],2) + round(rfperf_gm12878_50kb_none[7,2],2))/2, #balanced accuracy

                                round(rfperf_K562_50kb_none[9,2],2),
                                round(rfperf_K562_50kb_none[19,2],2),
                                round(rfperf_K562_50kb_none[16,2],2),
                                round(rfperf_K562_50kb_none[15,2],2),
								round(rfperf_K562_50kb_none[18,2],2),
								(round(rfperf_K562_50kb_none[6,2],2) + round(rfperf_K562_50kb_none[7,2],2))/2,

                                round(mean(rfperf_gm12878_50kb_rus[9,1]),2),
                                round(mean(rfperf_gm12878_50kb_rus[19,1]),2),
                                round(mean(rfperf_gm12878_50kb_rus[16,1]),2),
                                round(mean(rfperf_gm12878_50kb_rus[15,1]),2),
								round(mean(rfperf_gm12878_50kb_rus[18,1]),2),
								(round(mean(rfperf_gm12878_50kb_rus[6,1]),2) + round(mean(rfperf_gm12878_50kb_rus[7,1]),2))/2,

                                round(mean(rfperf_K562_50kb_rus[9,1]),2),
                                round(mean(rfperf_K562_50kb_rus[19,1]),2),
                                round(mean(rfperf_K562_50kb_rus[16,1]),2),
                                round(mean(rfperf_K562_50kb_rus[15,1]),2),
								round(mean(rfperf_K562_50kb_rus[18,1]),2),
								(round(mean(rfperf_K562_50kb_rus[6,1]),2) + round(mean(rfperf_K562_50kb_rus[7,1]),2))/2,

                                round(mean(rfperf_gm12878_50kb_ros[9,1]),2),
                                round(mean(rfperf_gm12878_50kb_ros[19,1]),2),
                                round(mean(rfperf_gm12878_50kb_ros[16,1]),2),
                                round(mean(rfperf_gm12878_50kb_ros[15,1]),2),
								round(mean(rfperf_gm12878_50kb_ros[18,1]),2),
								(round(mean(rfperf_gm12878_50kb_ros[6,1]),2) + round(mean(rfperf_gm12878_50kb_ros[7,1]),2))/2,

                                round(mean(rfperf_K562_50kb_ros[9,1]),2),
                                round(mean(rfperf_K562_50kb_ros[19,1]),2),
                                round(mean(rfperf_K562_50kb_ros[16,1]),2),
                                round(mean(rfperf_K562_50kb_ros[15,1]),2),
								round(mean(rfperf_K562_50kb_ros[18,1]),2),
								(round(mean(rfperf_K562_50kb_ros[6,1]),2) + round(mean(rfperf_K562_50kb_ros[7,1]),2))/2,

                                round(mean(rfperf_gm12878_50kb_smote[9,1]),2),
                                round(mean(rfperf_gm12878_50kb_smote[19,1]),2),
                                round(mean(rfperf_gm12878_50kb_smote[16,1]),2),
                                round(mean(rfperf_gm12878_50kb_smote[15,1]),2),
								round(mean(rfperf_gm12878_50kb_smote[18,1]),2),
								(round(mean(rfperf_gm12878_50kb_smote[6,1]),2) + round(mean(rfperf_gm12878_50kb_smote[7,1]),2))/2,

                                round(mean(rfperf_K562_50kb_smote[9,1]),2),
                                round(mean(rfperf_K562_50kb_smote[19,1]),2),
                                round(mean(rfperf_K562_50kb_smote[16,1]),2),
                                round(mean(rfperf_K562_50kb_smote[15,1]),2),
								round(mean(rfperf_K562_50kb_smote[18,1]),2),
								(round(mean(rfperf_K562_50kb_smote[6,1]),2) + round(mean(rfperf_K562_50kb_smote[7,1]),2))/2,

                                round(mean(rfperf_gm12878_50kb_rose[9,1]),2),
                                round(mean(rfperf_gm12878_50kb_rose[19,1]),2),
                                round(mean(rfperf_gm12878_50kb_rose[16,1]),2),
                                round(mean(rfperf_gm12878_50kb_rose[15,1]),2),
								round(mean(rfperf_gm12878_50kb_rose[18,1]),2),
								(round(mean(rfperf_gm12878_50kb_rose[6,1]),2) + round(mean(rfperf_gm12878_50kb_rose[7,1]),2))/2,

                                round(mean(rfperf_K562_50kb_rose[9,1]),2),
                                round(mean(rfperf_K562_50kb_rose[19,1]),2),
                                round(mean(rfperf_K562_50kb_rose[16,1]),2),
                                round(mean(rfperf_K562_50kb_rose[15,1]),2),
								round(mean(rfperf_K562_50kb_rose[18,1]),2),
								(round(mean(rfperf_K562_50kb_rose[6,1]),2) + round(mean(rfperf_K562_50kb_rose[7,1]),2))/2)

#all50kbresults$Resampling <- factor(all50kbresults$Resampling, levels=c("None", "RUS", "ROS", "SMOTE", "ROSE"))
#all50kbresults$CL <- factor(all50kbresults$CL, levels=c("GM12878", "K562"))
#all50kbresults$Metric <- factor(all50kbresults$Metric, levels=c("Accuracy", "AUPRC", "F1-Score", "MCC"))

@@

#comparing only informedness and balanced accuracy
informBA50kbplot <- ggplot(all50kbresults[which(all50kbresults$Metric=="Informedness" |
                                               all50kbresults$Metric=="Balanced Acc"),],
                       aes(x=Resampling, y=Performance, fill=CL)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("Resampling Technique") +
  ylim(0,.8)+
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Cell Line")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

@@

all100kbresults <- data.frame(Resampling=c(rep("None", 12),
                                       rep("RUS", 12),
                                       rep("ROS", 12),
                                       rep("SMOTE", 12),
                                       rep("ROSE", 12)),
                          CL=rep(c(rep("GM12878", 6),
                               rep("K562", 6)),5),
                          Metric=rep(c("Accuracy", 
                                       "AUPRC", 
                                       "F1-Score", 
                                       "MCC",
                                       "Informedness",
                                       "Balanced Acc"), 10))

all100kbresults$Performance <- c(round(rfperf_gm12878_100kb_none[9,2],2), #accuracy
                                round(rfperf_gm12878_100kb_none[19,2],2), #auprc
                                round(rfperf_gm12878_100kb_none[16,2],2), #f1
                                round(rfperf_gm12878_100kb_none[15,2],2), #mcc
								round(rfperf_gm12878_100kb_none[18,2],2), #youden
								(round(rfperf_gm12878_100kb_none[6,2],2) + round(rfperf_gm12878_100kb_none[7,2],2))/2, #balanced accuracy

                                round(rfperf_K562_100kb_none[9,2],2),
                                round(rfperf_K562_100kb_none[19,2],2),
                                round(rfperf_K562_100kb_none[16,2],2),
                                round(rfperf_K562_100kb_none[15,2],2),
								round(rfperf_K562_100kb_none[18,2],2),
								(round(rfperf_K562_100kb_none[6,2],2) + round(rfperf_K562_100kb_none[7,2],2))/2,

                                round(mean(rfperf_gm12878_100kb_rus[9,1]),2),
                                round(mean(rfperf_gm12878_100kb_rus[19,1]),2),
                                round(mean(rfperf_gm12878_100kb_rus[16,1]),2),
                                round(mean(rfperf_gm12878_100kb_rus[15,1]),2),
								round(mean(rfperf_gm12878_100kb_rus[18,1]),2),
								(round(mean(rfperf_gm12878_100kb_rus[6,1]),2) + round(mean(rfperf_gm12878_100kb_rus[7,1]),2))/2,

                                round(mean(rfperf_K562_100kb_rus[9,1]),2),
                                round(mean(rfperf_K562_100kb_rus[19,1]),2),
                                round(mean(rfperf_K562_100kb_rus[16,1]),2),
                                round(mean(rfperf_K562_100kb_rus[15,1]),2),
								round(mean(rfperf_K562_100kb_rus[18,1]),2),
								(round(mean(rfperf_K562_100kb_rus[6,1]),2) + round(mean(rfperf_K562_100kb_rus[7,1]),2))/2,

                                round(mean(rfperf_gm12878_100kb_ros[9,1]),2),
                                round(mean(rfperf_gm12878_100kb_ros[19,1]),2),
                                round(mean(rfperf_gm12878_100kb_ros[16,1]),2),
                                round(mean(rfperf_gm12878_100kb_ros[15,1]),2),
								round(mean(rfperf_gm12878_100kb_ros[18,1]),2),
								(round(mean(rfperf_gm12878_100kb_ros[6,1]),2) + round(mean(rfperf_gm12878_100kb_ros[7,1]),2))/2,

                                round(mean(rfperf_K562_100kb_ros[9,1]),2),
                                round(mean(rfperf_K562_100kb_ros[19,1]),2),
                                round(mean(rfperf_K562_100kb_ros[16,1]),2),
                                round(mean(rfperf_K562_100kb_ros[15,1]),2),
								round(mean(rfperf_K562_100kb_ros[18,1]),2),
								(round(mean(rfperf_K562_100kb_ros[6,1]),2) + round(mean(rfperf_K562_100kb_ros[7,1]),2))/2,

                                round(mean(rfperf_gm12878_100kb_smote[9,1]),2),
                                round(mean(rfperf_gm12878_100kb_smote[19,1]),2),
                                round(mean(rfperf_gm12878_100kb_smote[16,1]),2),
                                round(mean(rfperf_gm12878_100kb_smote[15,1]),2),
								round(mean(rfperf_gm12878_100kb_smote[18,1]),2),
								(round(mean(rfperf_gm12878_100kb_smote[6,1]),2) + round(mean(rfperf_gm12878_100kb_smote[7,1]),2))/2,

                                round(mean(rfperf_K562_100kb_smote[9,1]),2),
                                round(mean(rfperf_K562_100kb_smote[19,1]),2),
                                round(mean(rfperf_K562_100kb_smote[16,1]),2),
                                round(mean(rfperf_K562_100kb_smote[15,1]),2),
								round(mean(rfperf_K562_100kb_smote[18,1]),2),
								(round(mean(rfperf_K562_100kb_smote[6,1]),2) + round(mean(rfperf_K562_100kb_smote[7,1]),2))/2,

                                round(mean(rfperf_gm12878_100kb_rose[9,1]),2),
                                round(mean(rfperf_gm12878_100kb_rose[19,1]),2),
                                round(mean(rfperf_gm12878_100kb_rose[16,1]),2),
                                round(mean(rfperf_gm12878_100kb_rose[15,1]),2),
								round(mean(rfperf_gm12878_100kb_rose[18,1]),2),
								(round(mean(rfperf_gm12878_100kb_rose[6,1]),2) + round(mean(rfperf_gm12878_100kb_rose[7,1]),2))/2,
